Meta-analysis

### 2019-09-19 05_MetaAnalysis.Rmd

```{r variance}
# Trials using tebuconazole
PM_MB_means %>%
   filter(fungicide_ai == "tebuconazole",
         row_spacing.m == 0.75) %>%
   group_by(trial_ref, location, y_error.type) %>%
   summarise(tebuconazole_trts = length(y_error.type))

@@

@@

# plot of the mixed effect model, Black line shows the mean lmer regression line
ggplot(PM_MB_train) +
   geom_point(aes(y = yield_error, x = grain_yield.t.ha, colour = trial_ref)) +
   geom_abline(
      intercept = c(InterC, lmer.coef$trial_ref[, 1]),
      slope = c(paramA, lmer.coef$trial_ref[, 2]),
      size = 1,
      colour = c("Black", hue_pal()(16))
   ) +
   coord_cartesian(xlim = c(0, 3)) +
   theme_usq()
```

```{r na2Sv_formula}
for (i in NATrials$trial_ref) {
   #Sv <- (log(PM_MB_means[PM_MB_means$trial_ref == i,]$`grain_yield.t.ha`) - InterC)/ paramA  # parameter from when I had the predictor and response variable flipped

   Sv <-
      (PM_MB_means[PM_MB_means$trial_ref == i,]$`grain_yield.t.ha` * paramA) + InterC

   PM_MB_means[PM_MB_means$trial_ref == i,]$yield_error <- Sv
   PM_MB_means[PM_MB_means$trial_ref == i,]$y_error.type <-
      "SamplingVariance"
}
```

@@

# plot the data with the predicted slopes overlayed
ggplot(PM_MB_train.2) +
   geom_point(aes(y = yield_error, x = grain_yield.t.ha, colour = trial_ref)) +
   geom_abline(
      intercept = c(InterC, lmer.coef$trial_ref[, 1]),
      slope = c(paramA, lmer.coef$trial_ref[, 2]),
      size = 1,
      colour = c("Black", hue_pal()(15))
   ) +
   coord_cartesian(ylim = c(0, 0.33)) +
   xlab("Grain Yield (t/ha)") +
   ylab("Yield Error") +
   scale_colour_discrete("Trial Reference") +
   theme_usq()
```

@@

```{r random_slope_model}
# Run a linear model with yield error as a fixed effect predictor and trial as a random intercept
PM_MB_trainLMERx <- lmer(yield_error ~ 1 +
                            (grain_yield.t.ha |
                                trial_ref), data = PM_MB_train)

@@

# plot of the mixed effect model, Black line shows the mean lmer regression line
ggplot(PM_MB_train) +
   geom_point(aes(y = yield_error, x = grain_yield.t.ha, colour = trial_ref)) +
   geom_abline(
      intercept = lmer.coefx$trial_ref[, 2],
      slope = lmer.coefx$trial_ref[, 1],
      size = 1,
      colour = hue_pal()(16)
   ) +
   coord_cartesian(xlim = c(0, 3),
                   ylim = c(0, 1)) +
   xlab("Grain Yield (t/ha)") +
   ylab("Yield Error") +
   scale_colour_discrete("Trial Reference") +
   theme_usq()
```

After much deliberation I don't think this is possible to use the model with grain yield t/ha as a random slope. Even though we know the grain yields and the mean of the grain yields, we still can't predict the effect of the random intercept trial on the yield error.

@@

Emerson proposed I look at the between trial variation.

```{r between_trial_variation}
levels(factor(PM_MB_means$y_error.type))

PM_MB_means.SV <-
   filter(PM_MB_means, y_error.type == "SamplingVariance")

meta_mean.GY <- mean(PM_MB_means.SV$grain_yield.t.ha, na.rm = TRUE)

PM_MB_means_T <- PM_MB_means.SV %>%
   group_by(trial_ref) %>%
   summarise(
      trial_mean = mean(grain_yield.t.ha, na.rm = TRUE),
      BW_trial_variance = sd(grain_yield.t.ha, na.rm = TRUE) ^ 2
   )

PM_MB_means <- left_join(PM_MB_means, PM_MB_means_T, by = "trial_ref")

summary(lm(BW_trial_variance ~ trial_mean, data = PM_MB_means))
summary(lm(
   BW_trial_variance ~ trial_mean,
   data = subset(PM_MB_means, fungicide_ai == "tebuconazole")
))
summary(lm(
   BW_trial_variance ~ trial_mean,
   data = subset(PM_MB_means, fungicide_ai == "propiconazole")
))

plot(BW_trial_variance ~ trial_mean, data = PM_MB_means)
abline(-0.01356, 0.03076)
```

>>>>

```{r variance}

# Trials using tebuconazole
PM_MB_means %>%
   filter(fungicide_ai == "tebuconazole",
         row_spacing.m == 0.75) %>%
   group_by(trial_ref, location, y_error.type) %>%
   summarise(tebuconazole_trts = length(y_error.type))

@@

length(unique(PM_MB_train$Trial_ref))

@@

# for(i in NATrials$Trial_ref){
# #Sv <- (log(PM_MB_means[PM_MB_means$Trial_ref == i,]$`grain_yield.t.ha.`) - InterC)/ paramA  # parameter from when I had the predictor and response variable flipped
# 
# Sv <- (PM_MB_means[PM_MB_means$Trial_ref == i,]$`grain_yield.t.ha.` * paramA) + InterC
# 
# PM_MB_means[PM_MB_means$Trial_ref == i,]$Yield_error <- Sv
# PM_MB_means[PM_MB_means$Trial_ref == i,]$Y_error.type <- "SamplingVariance"
# }

# plot of the mixed effect model, Black line shows the mean lmer regression line
ggplot(PM_MB_train) +
   geom_point(aes(y = yield_error, x = grain_yield.t.ha, colour = trial_ref)) +
   geom_abline(
      intercept = c(InterC, lmer.coef$trial_ref[, 1]),
      slope = c(paramA, lmer.coef$trial_ref[, 2]),
      size = 1,
      colour = c("Black", hue_pal()(length(unique(PM_MB_train$trial_ref))))
   ) +
   coord_cartesian(xlim = c(0, 3)) +
   theme_usq()
```

```{r na2Sv_formula}
# commented until a reliable model can be written

# for (i in NATrials$trial_ref) {
#    #Sv <- (log(PM_MB_means[PM_MB_means$trial_ref == i,]$`grain_yield.t.ha`) - InterC)/ paramA  # parameter from when I had the predictor and response variable flipped
#    
#    Sv <-
#       (PM_MB_means[PM_MB_means$trial_ref == i,]$`grain_yield.t.ha` * paramA) + InterC
#    
#    PM_MB_means[PM_MB_means$trial_ref == i,]$yield_error <- Sv
#    PM_MB_means[PM_MB_means$trial_ref == i,]$y_error.type <-
#       "SamplingVariance"
# }

```

@@

# plot the data with the predicted slopes overlayed

ggplot(PM_MB_train.2) +
   geom_point(aes(y = yield_error, x = grain_yield.t.ha, colour = trial_ref)) +
   geom_abline(
      intercept = c(InterC, lmer.coef$trial_ref[, 1]),
      slope = c(paramA, lmer.coef$trial_ref[, 2]),
      size = 1,
      colour = c("Black", hue_pal()(length(unique(PM_MB_train.2$Trial_ref))))
   ) +
   coord_cartesian(ylim = c(0, 0.33)) +
   xlab("Grain Yield (t/ha)") +
   ylab("Yield Error") +
   scale_colour_discrete("Trial Reference") +
   theme_usq()

```

@@

```{r random_slope_model} 
# This code chunk broke with the addition of new data, I will re-inspect the data and remodel.

# Run a linear model with yield error as a fixed effect predictor and trial as a random intercept
PM_MB_trainLMERx <- lmer(yield_error ~ 1 +
                            (grain_yield.t.ha |
                                trial_ref), data = PM_MB_train)

@@

# plot of the mixed effect model, Black line shows the mean lmer regression line
ggplot(PM_MB_train) +
   geom_point(aes(y = yield_error, x = grain_yield.t.ha, colour = trial_ref)) +
   geom_abline(
      intercept = lmer.coefx$trial_ref[, 2],
      slope = lmer.coefx$trial_ref[, 1],
      size = 1,
      colour = hue_pal()(length(unique(PM_MB_train$Trial_ref)))
   ) +
   coord_cartesian(xlim = c(0, 3),
                   ylim = c(0, 1)) +
   xlab("Grain Yield (t/ha)") +
   ylab("Yield Error") +
   scale_colour_discrete("Trial Reference") +
   theme_usq()
```
After much deliberation I don't think this is possible to use the model with grain yield t/ha as a random slope. Even though we know the grain yields and the mean of the grain yields, we still can't predict the effect of the random intercept trial on the yield error.

@@

Emerson proposed I look at the between trial variation
```{r between_trial_variation}
levels(factor(PM_MB_means$Y_error.type))

PM_MB_means.SV <- PM_MB_means[PM_MB_means$Y_error.type == "SamplingVariance",]
meta_mean.GY <- mean(PM_MB_means.SV$grain_yield.t.ha.,na.rm = TRUE)

# find the mean and variance of each trial
PM_MB_means_T <- PM_MB_means %>%
   filter(Y_error.type == "SamplingVariance") %>%
   group_by(trial_ref) %>%
   summarise(trial_mean = mean(grain_yield.t.ha, na.rm = TRUE),
             BW_trial_variance = sd(grain_yield.t.ha, na.rm = TRUE) ^ 2
             ) # I am not sure I have calculated between trial variance or trial variance// Should I be using a denominator (N-1) or (N), sd by default uses (N-1)

# update the main data set with Trial variance
SV_Trials <- unique(PM_MB_means_T$Trial_ref)
PM_MB_means$TrialVariance <- NA

for(i in SV_Trials){
   PM_MB_means[PM_MB_means$Trial_ref == i, "TrialVariance"] <- PM_MB_means_T[PM_MB_means_T$Trial_ref == i,"Trial_variance"]
}
PM_MB_means$TrialVariance
# OR ?
PM_MB_means <- left_join(PM_MB_means, PM_MB_means_T, by = "trial_ref")

SV_mod1 <- lm(Trial_variance ~ trial_mean, data = PM_MB_means_T)
summary(SV_mod1)

plot(Trial_variance ~ trial_mean, data = PM_MB_means_T)
abline(SV_mod1)

```
